Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Use evidence instead of example/property
Fix typo
Add important points that should go into the "Introduction"

%%%% Describe the problem.

@@

\item
    Introduce a set of combinators to set of expectations about \emph{code
    examples} for use with \hspec{}.
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and
    \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Examples/properties for users}
\label{sec:for-users}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Examples/properties for developers}
\label{sec:for-developers}

>>>>

%%%% Describe the problem.
\begin{quote}
    Important points we want to say:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
    \end{itemize}
\end{quote}

@@

\item
    Introduce a set of combinators to set expectations about \emph{code
    examples} for use with \hspec{}.
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and
    \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as user documentation}
\label{sec:for-users}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as code documentation}
\label{sec:for-developers}
